Determining Causes of Death from Verbal Autopsy with ChatGPT: A Case Study of 6942 Deaths in Sierra Leone from 2019-2022

### 2024-01-21 manuscript/manuscript.tex
Add csmfa methods, add andy/paijani to paper

\author*[1]{\fnm{Richard} \sur{Wen}}\email{richard.wen@unityhealth.to}

@@

@@

CSMF accuracy measures the performance of models at the population level, comparing distributions of CODs between the physicians and the models \cite{murrayRobustMetricsAssessing2011}. CSMF is the number of records $N_j$ for cause $j$ divided by the total number of records $N$ (Equation \ref{eq-csmf}).

\begin{equation}\label{eq-csmf}
    CSMF_j = N_j / N
\end{equation}

\begin{equation}
    CSMFMaximumError = 2(1 - Min(CSMF^{true}_j)
\end{equation}

\begin{equation}
    CSMFAccuracy = 1 - \frac{\sum^{k}_{j=1}|CSMF^{true}_j - CSMF^{pred}_j|}{CSMFMaximumError}
\end{equation}

@@

>>>>

\author*[1,2]{\fnm{Richard} \sur{Wen}}\email{richard.wen@unityhealth.to}

@@

\author[1]{\fnm{Andy} \sur{Lee}}\email{Andy.Lee2@unityhealth.to}

\author[1,2]{\fnm{Paijani} \sur{Sheth}}\email{paijani.sheth@mail.utoronto.ca}

@@

CSMF accuracy measures the performance of models at the population level, comparing distributions of CODs between the physicians and the models \cite{murrayRobustMetricsAssessing2011}. To calculate CSMF accuracy, we first calculate $CSMF_j$ as is the fraction of physician or model records for cause $j$, given by dividing the number of records for cause $j$ with the total number of records as seen in Equation \ref{eq-csmf}. Then, the $CSMFMaximumError$, representing the worst possible model, is calculated using Equation \ref{eq-csmferr}. Finally, the CSMF accuracy is given by Equation \ref{eq-csmfa}, where $k$ is the number of causes, $j$ is a cause, $CSMF^{true}_j$ is the true physician CSMF for cause $j$, and $CSMF^{pred}_j$ is the predicted model CSMF for cause $j$. CSMF accuracy ranges from 0 to 1, where 1 means that the model completely matched the physician COD distribution and 0 means that it did not match the distribution at all.

\begin{equation}\label{eq-csmf}
    CSMF_j = Records_j / Records
\end{equation}

\begin{equation}\label{eq-csmferr}
    CSMFMaximumError = 2(1 - Min(CSMF^{true}_j)
\end{equation}

\begin{equation}\label{eq-csmfa}
CSMFAccuracy = 1 - \frac{\sum^{k}_{j=1}|CSMF^{true}_j - CSMF^{pred}_j|}{CSMFMaximumError}
\end{equation}

@@

PCCC measures the performance of models at the individual level, comparing COD assignments between the physicians and models on a record by record basis, and how much better it is than random assignment \cite{murrayRobustMetricsAssessing2011}:
